The {\sc VSPEC} code: Spectroscopic phase curves of 3D exoplanet models in the presence of stellar variability

### 2024-06-06 src/tex/ms.tex
Add Avi's additions from overleaf

% Abstract with filler text
\begin{abstract}
    We present the Variable Star Phase Curve (\href{https://github.com/VSPEC-collab/VSPEC}{ \sc VSPEC}) code,
    a python package to simulate spectroscopic observations of rocky exoplanets in the presence of stellar variability.
    {\sc VSPEC} uses the Planetary Spectrum Generator's Global Emission Spectra (PSG GlobES) application along with a custom-built
    stellar model to produce spectroscopic light curves of the planet-host system. We also describe associated codes. \TJ{These codes should be named here and described a little}
\end{abstract}

@@

In the era of high-sensitivity exoplanet characterization missions such as the James Webb Space Telescope (JWST)
and the Atmospheric Remote-sensing Infrared Exoplanet Large-survey (ARIEL), spectral analysis of exoplanet atmospheres
is increasingly sensitive to contamination due to stellar inhomogenies (spots, granulation, etc.).

Recent analysis of the JWST/NIRSpec transit of GJ 486b by \citet{moran2023} exposed a degeneracy between
atmospheric absorption by water and water-rich spots on the stellar surface. This ``transit light source effect''
\citep[TLS,][see also \citet{apai2018,barclay2021,garcia2022,barclay2023}]{rackham2018}
occurs when the occulted region of the stellar surface is not representitive of the disk-integrated spectrum

@@

We present {\sc VSPEC}: Variable Star PhasE Curve\footnote{\url{https://github.com/VSPEC-collab/VSPEC}},
an open-source Python 3 package to simulate observations of exoplanet systems with variable host stars.
{\sc VSPEC} combines NASA's Planetary Spectrum Generator \citep[PSG,][]{villanueva2018} with a grid of
custom PHOENIX models \citep{husser2013} to produce multiwavelength phase curves of the system, accounting
for a 3D planetary atmosphere, transits and eclipses, and multiple sources of stellar variability.

>>>>

% Abstract with filler text
\begin{abstract}
    We present the Variable Star Phase Curve (\href{https://github.com/VSPEC-collab/VSPEC}{ \sc VSPEC}) code,
    a python package to simulate combined-light spectroscopic observations of exoplanets in the presence of stellar variability and inhomogeneity.
    {\sc VSPEC} uses the Planetary Spectrum Generator's Global Emission Spectra (PSG GlobES) application along with a custom-built
    stellar model based on an existing grid of stellar photosphere models to produce spectroscopic light curves of the planet-host system.
    VSPEC can be a useful tool for modeling observations of exoplanets in transiting geometries (primary transit, secondary eclipse) as well as orbital phase curve measurements,
    and is built in a modular and flexible configuration for easy adaptability to new stellar and planetary model inputs.
    We also describe associated codes. \TJ{These codes should be named here and described a little}
\end{abstract}

@@

In the era of high-sensitivity exoplanet characterization missions such as the James Webb Space Telescope (JWST)
and the Atmospheric Remote-sensing Infrared Exoplanet Large-survey (ARIEL), spectral analysis of exoplanet atmospheres
is increasingly sensitive to contamination due to stellar inhomogeneities (e.g. spots, granulation) and stochastic stellar variability (e.g. flares).

Recent analysis of the JWST/NIRSpec transit of GJ 486b by \citet{moran2023} exposed a degeneracy between
atmospheric absorption by water and water-rich spots on the stellar surface. This ``transit light source effect''
\citep[TLS,][see also \citet{apai2018,barclay2021,garcia2022,barclay2023}]{rackham2018}
occurs when the occulted region of the stellar surface is not representative of the disk-integrated spectrum.

@@

In this paper we present present {\sc VSPEC}: Variable Star PhasE Curve\footnote{\url{https://github.com/VSPEC-collab/VSPEC}},
an open-source Python 3 package to simulate observations of exoplanet systems with variable host stars.
{\sc VSPEC} combines NASA's Planetary Spectrum Generator \citep[PSG,][]{villanueva2018} with a grid of
custom PHOENIX models \citep{husser2013} to produce multiwavelength phase curves of the system, accounting
for a 3D planetary atmosphere, transits and eclipses, and multiple sources of stellar variability.
